Manuscript_Github_Pchabaudi_pir

### 2021-03-15 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Added supp fig names and reorder figures

### 2D plot of PC1 v PC2 - Supp figure 4A

@@

# Phaseograms of the data.

@@

## Phaseograms of the _cir_ genes with clade annotations.

@@

## Figure 3b - Highest expressed all _pir_ heatmap

```{r figure_3b_suppinfo}

combined_data_pir_ht <- getElement(combined_data_pir_ht_list,
                                            'rMT')

supp_info_fig_3b <- lapply(names(combined_data_pir_ht_list),
       function(list_name){

         colnames(combined_data_pir_ht) <- paste0(list_name, 
                                                  '_', 
                                                  colnames(combined_data_pir_ht))

         log2(1+combined_data_pir_ht)[pir_highest_tpm_order,]
       }) %>% 
  bind_cols

supp_info_fig_3b$SorL <- cir_info$SorL[match(names(apply(supp_info_fig_3b, 1, mean)), 
                                                   cir_info$Geneid)]

head(supp_info_fig_3b)

>>>>

## Figure 3c and Supp figure 3 - Highest expressed all _pir_ heatmap

## 2D plot of PC1 v PC2 - Supp figure 4A

@@

# Phaseograms of all the genes in both transmission methods - supplementary figure 5.

@@

## Phaseograms of the _cir_ genes with clade annotations. - Supplementary figure 6

@@
